Model-based variable selection for regression with highly correlated variables.

### 2014-05-27 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@623 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
up bv MSE
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@624 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	The objective here is not only to predict non-quality but to understand and then avoid it. CorReg provides an automatic method without any a priori and is combined with variable selection methods. So it allows to obtain in a small amount of time some indications on the source of the problem, and to use human resources efficiently. When quality crises occurs, time is extremely precious so automation is a real stake.

@@

\begin{figure}[h!]
	\begin{minipage}[l]{.30\linewidth}
			\includegraphics[width=150px]{figures/correlbeforeafter.png} 
			\caption{Correlations between the covariates in $\boldsymbol{X}$ (upper) and $\hat{\boldsymbol{X}}_f$ (lower).}
	\end{minipage} \hfill
	\begin{minipage}[c]{.30\linewidth}
			\includegraphics[height=150px, width=150px]{figures/R2corregBVBI.png} 
			\caption{$R^2_{adj}$ of the 67 sub-regressions.}
	\end{minipage} \hfill
   \begin{minipage}[r]{.30\linewidth}
			\includegraphics[height=150px,width=150px]{figures/histcorrelBVBI.png} 
			\caption{Histogram of correlations in $\boldsymbol{X}$.} 
   \end{minipage}
\end{figure}   			
%	Here $n<p$ so we only compare the leave-one-out cross-validation MSE.
%	\textsc{CorReg} improves LASSO by $5.24\%$ and elasticnet by $8.60\%$. \textsc{CorReg} combined with LASSO gives the best result but it is only a leave-on-out MSE.
%\begin{table}[h!]
%\centering
%\begin{tabular}{|c|c|c|}
%	\hline 
%	Model & MSE & Complexity (with intercept) \\ 
%	\hline 
%	LASSO & 105.54 & 34 \\ 
%	\hline 
%	\textsc{CorReg} + LASSO & 100 & 18 \\ 
%	\hline 
%	elasticnet & 129.94 & 13 \\ 
%	\hline 
%	\textsc{CorReg} + elasticnet & 118.76 & 21 \\ 
%	\hline 
%\end{tabular} 
%\caption{Results obtained with leave-one out cross-validation. $n=100, p=145$.}	
%\end{table}
The response variable was binary but $n$ was too small compared to $p$ to use logistic regression so we have considered $\boldsymbol{Y}$ as a continuous variable and then made imputation by $1$ when $\hat{\boldsymbol{Y}}>0.5$ and by $0$ else.

\begin{table}[h!]
\centering
\begin{tabular}{|c c|c|c|}
	\hline 
	Method& indicator& With CorReg & without CorReg \\ 
	\hline
	OLS & well-classified & 100& 56 \\
		& MSE (leave-one-out) & & \\
		& complexity & 91& 100 \\
	\hline 
		LASSO & well-classified &93 &93 \\
		& MSE (leave-one-out) & 0.106 & 0.120\\
		& complexity & 27&34\\
	\hline 
		Elasticnet & well-classified &84 &87 \\
		& MSE (leave-one-out) &0.140 &0.148\\
		& complexity &10 &13\\
	\hline 
		Ridge & well-classified &88 &85 \\
		& MSE (leave-one-out) & &\\
		& complexity &91 &146\\
	\hline 
\end{tabular} 
\caption{Results obtained with leave-one out cross-validation. $n=100, p=145$.}	
\end{table}

>>>>

	The objective here is not only to predict non-quality but to understand and then avoid it. CorReg provides an automatic method without any a priori and is combined with variable selection methods. So it allows to obtain in a small amount of time some indications on the source of the problem, and to use human resources efficiently. When quality crises occurs, time is extremely precious so automation is a real stake. The combinatorial aspect of the sub-regression models makes it impossible to do manually.

@@

\begin{figure}[h!]
	\begin{minipage}[l]{.30\linewidth}
			\includegraphics[width=150px]{figures/correlbeforeafter.png} 
			\caption{Correlations between the covariates in $\boldsymbol{X}$ (upper) and $\hat{\boldsymbol{X}}_f$ (lower).}
	\end{minipage} \hfill
	\begin{minipage}[c]{.30\linewidth}
				\includegraphics[height=150px,width=150px]{figures/histcorrelBVBI.png} 
			\caption{Histogram of correlations in $\boldsymbol{X}$.} 
	\end{minipage} \hfill
   \begin{minipage}[r]{.30\linewidth}
			\includegraphics[height=150px, width=150px]{figures/R2corregBVBI.png} 
			\caption{$R^2_{adj}$ of the 55 sub-regressions.}\label{R2bv}
   \end{minipage}
\end{figure}   	
CorReg found 55 sub-regressions as shown in Figure \ref{R2bv}. One of them seems to be weak $R^2=0.17$ but is not linear (points out a link between diameter of a coil and some shape indicator).

The response variable was binary but $n$ was too small compared to $p$ to use logistic regression so we have considered $\boldsymbol{Y}$ as a continuous variable and then made imputation by $1$ when $\hat{\boldsymbol{Y}}>0.5$ and by $0$ else.

\begin{table}[h!]
\centering
\begin{tabular}{|c c|c|c|}
	\hline 
	Method& indicator& With CorReg & without CorReg \\ 
	\hline
	OLS & well-classified & 100& 56 \\
		& MSE (leave-one-out)& 1.95& 51 810\\
		& complexity & 91& 100 \\
	\hline 
		LASSO & well-classified &93 &93 \\
		& MSE (leave-one-out)& 0.106 & 0.120\\
		& complexity & 27&34\\
	\hline 
		Elasticnet & well-classified &84 &87 \\
		& MSE (leave-one-out)&0.140 &0.148\\
		& complexity &10 &13\\
	\hline 
		Ridge & well-classified &88 &85 \\
		& MSE (leave-one-out)& 0.179 & 0.177\\
		& complexity &91 &146\\
	\hline 
\end{tabular} 
\caption{Results obtained with leave-one out cross-validation. $n=100, p=145$.}	
\end{table}
